Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/case-study.tex

In total, eight cyber requirements are generated and imported into our model.  These include one \textit{sandboxing} requirement, four \textit{well-formedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the ground station software has not been tampered with.  Requirements are imported into the model as goals in a Resolute assurance case.  Because we can run Resolute at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

@@

Similar to the filters, the monitor policies are specified in AGREE. The Response Monitor specification is shown in Figure~\ref{fig:response-monitor}, and the Geofence Monitor specification is shown in Figure\ref{fig:geofence-monitor}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/response-monitor.png}
	\caption{Response Monitor specification.} 
	\label{fig:response-monitor} 
\end{figure}

@@

% Describe attestation?

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/hardened-sw.png}
	\caption{Cyber-resilient software architecture.} 
	\label{fig:hardened-sw} 
\end{figure*}

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication and is consistent with the AADL specification computational model.

% Something about seL4?

>>>>

In total, eight cyber requirements are generated and imported into our model.  These include one \textit{sandboxing} requirement, four \textit{well-formedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in a Resolute assurance case.  Because we can run Resolute at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

@@

Similar to the filters, the monitor policies are specified in AGREE. For example, 
%The Response Monitor specification is shown in Figure~\ref{fig:response-monitor}, and 
the Geofence Monitor specification is shown in Figure\ref{fig:geofence-monitor}.

% \begin{figure}[h]
% 	\centering
% 	\includegraphics[width=1\columnwidth]{figs/response-monitor.png}
% 	\caption{Response Monitor specification.} 
% 	\label{fig:response-monitor} 
% \end{figure}

@@

The requirements that have been addressed so far mitigate vulnerabilities related to malformed messages and malicious behavior \textit{on board} the UAV.  But we also want to protect against a compromised Ground Station that could potentially transmit well-formed, but malicious commands. The final cyber-requirement is mitigated by the Attestation transform~\cite{attestation-copland}, which adds two components to the UAV software: an Attestation Manager for evaluating remote systems like the Ground Station, and an Attestation Gate for filtering messages from sources that have not been approved by the Attestation Manager.  The Attestation Manager is implemented in CakeML and automatically inserted into the application code base by BriefCASE.  Because the Attestation Gate acts as a filter, the transform automatically generates its complete AGREE specification.%, as shown in Figure~\ref{fig:attestation}.

% \begin{figure}[h]
% 	\centering
% 	\includegraphics[width=1\columnwidth]{figs/attestation.png}
% 	\caption{Atestation specification.} 
% 	\label{fig:attestation} 
% \end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/hardened-sw.png}
	\caption{Cyber-resilient software architecture.} 
	\label{fig:hardened-sw} 
\end{figure}

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication and is consistent with the AADL specification computational model.
%
HAMR then compiles the software to execute on seL4~\cite{DBLP:journals/cacm/KleinAEHCDEEKNSTW10}, a
verified capability-based microkernel (accompanied by formal proof of
spatial isolation properties down to the binary level).

The UAV and Ground Station software were deployed on the ODROID XU4 hardware and communicated with each other over Ethernet.  The AMASE flight simulator, representing the Flight Contol Computer was run on a Linux machine and connected to the UAV ODROID via a serial connection.  The UxAS implementation on the UAV was modified by adding malicious code that would prevent it from responding to Automation Requests or produce flight plans that would violate the operating region constraints.  Some of the Line Search Task messages transmitted from the Ground Station contained malformed messages that would modify the UxAS behavior. In addition, we modified the Ground Station to simulate a breach for the attestation test.

We performed an initial set of tests on the un-hardened system (Figure~\ref{fig:sw-initial}) to verify the effectiveness of the malicious code.  The following scenarios were exercised:

\paragraph{Infected Ground Station} In this scenario, one of the UxAS files is modified on the Ground Station. When Ground Station files are modified in such an unauthorized manner, messages sent to the UAV will be rejected by the Attestation Manager.

\paragraph{Malformed Line Search Task message} In this scenario, the Line Search Task message contains a waypoint with a longitude value outside the permitted range.  Such malformed messages could exploit vulnerabilities in the onboard software.  This vulnerability is mitigated by inserting a well-formedness filter.  The filter prevents the Line Search Task message from reaching UxAS.

\paragraph{UxAS vulnerability exploit} In this scenario, Line Search Tasks with greater than 90 waypoints will trigger a vulnerability that will crash UxAS.   When this occurs, UxAS be prevented from generating an Automation Response.  This vulnerability is mitigated by inserting a Response Monitor, which checks to see that UxAS outputs an Automation Response message shortly after receiving an Automation Request.  For this scenario, we chose for the monitor to output a status message, which would then be received by the ground station and an appropriate action taken.

\paragraph{UxAS trojan modifies flight plan} In this scenario, a trojan embedded in UxAS will attempt to cause the UAV to fly into the specified keep-out zone by modifying the mission command waypoints in the Automation Response.  However, the UAV will detect that it is being instructed to fly into a keep-out zone and instead return to Home Base.

We repeated the tests on the hardened system and were able to demonstrate that our mitigations were successful, as shown in the status messages sent from the high-assurance components in Figure~\ref{fig:mitigation-output}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/mitigation-output.png}
	\caption{Cyber-resilient system response.} 
	\label{fig:mitigation-output} 
\end{figure}
